Some Nice Title Goes Here, Eventually\ldots

### 2014-08-30 doc/tacs2014/article.tex
Introduction section, revised problem description, new model overview figure

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
	\and
	\IEEEauthorblockN{Dr. Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:everardo.gutierrez@uabc.edu.mx}{\texttt{everardo.gutierrez@uabc.edu.mx}}}
}

@@

%\markboth{TACS 2014 and more info here}{} % Only on journal papers, apparently...

@@

@@

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	it becomes apparent that a monolithic system design would be both unwieldly and computationally expensive, requiring
	deep neural networks \cite{ciresan2012multi} to attain high recognition rates.

	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each component. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

@@

@@

	Should we mention alternative solutions, such as SVMs? Tomoe does quite a good job, for instance. Not sure if there
	are academic evaluations/references, though.

@@

	Some text here, followed by a diagram. Divide and conquer!

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/model-overview.eps}
		\caption{Model overview. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
		\label{fig_model_overview}
	\end{figure}

@@

@@

@@

@@

\begin{table}
	\renewcommand{\arraystretch}{1.3}
	\caption{Statistical overview of \ldots}
	\label{tbl_stroke_analysis}
	\centering
	\begin{tabular}{ c | c c c c c l }
		\hline
		  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & Highest count \\ 
		\hline
		\hline
		\bfseries A & $33.20\%$ & $26,160$ & $4.09$ & $2.33$ & $15$ & \\%(蠶) \\
		\bfseries B & $1.47\%$  & $1,159$  & $0.18$ & $0.40$ & $2$  & \\%(摑) \\
		\bfseries C & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
		\bfseries D & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
		\bfseries E & $0.31\%$  & $245$    & $0.04$ & $0.19$ & $2$  & \\%(霪) \\
		\bfseries F & $12.72\%$ & $10,018$ & $1.57$ & $1.36$ & $10$ & \\%(鏐) \\
		\bfseries G & $29.98\%$ & $23,616$ & $3.69$ & $1.96$ & $13$ & \\%(鱸) \\
		\bfseries H & $22.32\%$ & $17,587$ & $2.75$ & $1.61$ & $11$ & \\%(靆) \\
		\hline
		\hline
	\end{tabular}
\end{table}

	% Statistical representation was close to perfect after the initial
	% segment of some 3k kanji
	\begin{tikzpicture}[font=\small]
		\begin{axis}[
			ybar,
			bar width=20pt,
			xlabel={Stroke feature classification},
			ylabel={Frequency (\%)},
			ymin=0,
			ymax=40,
			%ytick=\empty,
			xtick=data,
			axis x line=bottom,
			axis y line=left,
			enlarge x limits=0.2,
			symbolic x coords={A, B, C, D, E, F, G, H},
			xticklabel style={anchor=base, yshift=-\baselineskip},
			nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
		]
			\addplot[fill=white] coordinates {
				(A, 33.2)
				(B, 1.5)
				(C, 0)
				(D, 0)
				(E, 0.3)
				(F, 12.7)
				(G, 30.0)
				(H, 22.3)
			};
		\end{axis}
	\end{tikzpicture}

	\subsection{Preliminary results}

@@

	%\section{References}
	\bibliography{./references}

>>>>

\author{
	\IEEEauthorblockN{Lars Fredrik Karlstr\"om}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:fredrik.karlstrm@uabc.edu.mx}{\texttt{fredrik.karlstrm@uabc.edu.mx}}}
	\and
	\IEEEauthorblockN{Everardo Guti\'errez L\'opez}
	\IEEEauthorblockA{Faculty of Science, Dept. of Computer Science\\ Universidad Aut\'onoma de Baja California\\ \href{mailto:everardo.gutierrez@uabc.edu.mx}{\texttt{everardo.gutierrez@uabc.edu.mx}}}
}

@@

@@

	\section{Introduction}

	%Although new technologies aimed at digitalizing every aspect of daily life are introduced and adopted at an ever--increasing pace,
	%handwriting still remains an integral

	Although a variety of efficient digital input methods have become all but second nature to recent generations, for the vast majority,
	handwriting remains an integral activity in daily life.
	The importance to further improve upon the state of the art in handwriting recognition is underlined not only by the continued prevalence of 
	handwriting, but also by the need to digitalize archived material, the significant role of handwriting in the development of fine motor skills,
	and a variety of other areas of application, such as signature verification. \cite{plamondon2000online}

	As an area of research, handwriting recognition predates even the digital computer. In 1888, Elisha Gray was awarded a patent \cite{gray1888telautograph}
	for the ``Telautograph,'' which is considered a precursor to the stylus and digitizer.
	In \cite{dimond1957devices} (1957), T.L. Dimond summarized early character recognition efforts and introduced the Stylator, another input recognition device.

	The decades of research since has introduced a vast number of recognition techniques for writing in any and all forms; notable successful techniques in
	widespread use today include support vector machines, hidden Markov models, and artificial neural networks. \cite{fujisawa2008forty} \cite{tappert1990state}

@@

	Given that the category search space for Japanese characters is an order of magnitude larger than its western counterparts,
	and that other characteristics must be taken into account, it becomes apparent that the same designs that
	yields highly accurate results on the western alphabet will not perform satisfactory when applied to asian character recognition, \cite{tappert1990state}
	unless it relies on complex, computationally expensive techniques such as for instance ``deep'' neural networks. \cite{ciresan2012multi}

	In this work, we describe a flexble, modular design scheme that splits the identification task into coarse and fine steps,
	thereby reducing the complexity of each undertaking. The design scheme also permits replacing classification strategies,
	and facilitates the parallelization of network training.

@@

	In \cite{yang2003accelerating}, clustering, offline recognition, first comparing input to centroid character,
	therafter search within.

@@

	Should we mention alternative solutions, such as SVMs? Zinnia (w/ Tomoe) does quite a good job, for instance. Not sure if there
	are academic evaluations/references, though.

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/model-overview.eps}
		\caption{The model consists of four components: a feature extractor, a clustering strategy,
			a router (coarse classifier), and a fine--grained classifier.}
		\label{fig_model_overview}
	\end{figure}

	By structuring the search space into mutually exclusive clusters of similar categories,
	we are able to construct a corresponding number of fine classifiers that need only distinguish
	between the categories within its own cluster. The smaller search space directly translates into a
	significant reduction of model complexity, which in turn implies both a decrease in training time
	and the possibility of higher accuracy rates. Furthermore, given that no category overlap exists
	between the clusters, each fine classifier may be trained in parallel, and each model may be gradually
	improved as new training data is made available.

@@

	The input data is processed by an algorithm, generating a coarse, n--dimensional representation of its principal features.
	The feature vector is used to select which cluster the input belongs to.

	A higher feature vector dimensionality allows for the construction of more finely--tuned clusters, but may well increase
	the likelihood of ``misrouting,'' resulting in a failed classification.
	% Actually, if a character is not found within the specified CANN, it could be passed to a neighboring cluster of similar composition

	The coarse classifier may work on either online or offline input, or potentially a union of them both.
	Examples of feature extractors include the LTM algorithm, and gradient--based solutions, both outlined in \cite{tanaka1999hybrid}.

@@

	\begin{figure}
		\centering
		\includegraphics[width=2.75in]{./fig/experimental-implementation.eps}
		\caption{Experimental implementation. The input is first analyzed by the coarse classifier, resulting in the $<GHA\ldots>$ feature representation.
		Thereafter, the routing network selects which cluster to search in, and the image data is passed to the corresponding CANN for fine--grain classification.}
		\label{fig_experimental_implementation}
	\end{figure}

	\subsection{Data sources}

	KanjiVG \ldots

	Figure of A-H compass. Explanation.

	\begin{table}
		\renewcommand{\arraystretch}{1.3}
		\caption{Stroke type frequency distribution overview }
		\label{tbl_stroke_analysis}
		\centering
		\begin{tabular}{ c | c c c c c l }
			\hline
			  & \bfseries \% & \small $\sum$ & $\mu$ & $\sigma$ & Highest count \\ 
			\hline
			\hline
			\bfseries A & $33.20\%$ & $26,160$ & $4.09$ & $2.33$ & $15$ & \\%(蠶) \\
			\bfseries B & $1.47\%$  & $1,159$  & $0.18$ & $0.40$ & $2$  & \\%(摑) \\
			\bfseries C & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
			\bfseries D & $0.00\%$  & $0$      & --     & --     & --   & \\%     \\
			\bfseries E & $0.31\%$  & $245$    & $0.04$ & $0.19$ & $2$  & \\%(霪) \\
			\bfseries F & $12.72\%$ & $10,018$ & $1.57$ & $1.36$ & $10$ & \\%(鏐) \\
			\bfseries G & $29.98\%$ & $23,616$ & $3.69$ & $1.96$ & $13$ & \\%(鱸) \\
			\bfseries H & $22.32\%$ & $17,587$ & $2.75$ & $1.61$ & $11$ & \\%(靆) \\
			\hline
			            & $100.00\%$   & $78,785$ &        &        &      & \\
			\hline
		\end{tabular}
	\end{table}

@@

	Based on the information summarized in table \ref{tbl_stroke_analysis}, \ldots

@@

	\begin{table}
		\renewcommand{\arraystretch}{1.3}
		\caption{Some form of cluster sample}
		\label{tbl_sample_clusters}
		\centering
		\begin{tabular}{c}
			We could list centroid info and some sample kanji. \\
			But not \emph{all} the clusters, right? Too many\ldots \\
		\end{tabular}
	\end{table}

	%\begin{tikzpicture}[font=\small]
	%	\begin{axis}[
	%		ybar,
	%		bar width=20pt,
	%		xlabel={Stroke feature classification},
	%		ylabel={Frequency (\%)},
	%		ymin=0,
	%		ymax=40,
	%		%ytick=\empty,
	%		xtick=data,
	%		axis x line=bottom,
	%		axis y line=left,
	%		enlarge x limits=0.2,
	%		symbolic x coords={A, B, C, D, E, F, G, H},
	%		xticklabel style={anchor=base, yshift=-\baselineskip},
	%		nodes near coords={\pgfmathprintnumber\pgfplotspointmeta}
	%	]
	%		\addplot[fill=white] coordinates {
	%			(A, 33.2)
	%			(B, 1.5)
	%			(C, 0)
	%			(D, 0)
	%			(E, 0.3)
	%			(F, 12.7)
	%			(G, 30.0)
	%			(H, 22.3)
	%		};
	%	\end{axis}
	%\end{tikzpicture}

	\section{Preliminary results}

@@

	% References
	\bibliography{./references}
